Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-22 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
Correcciones Hugo: en la intro this por these

While the standard setting in RL is to model the interaction agent-environment as an agent that moves from one \textit{state} to another inside a model of the environment and observing a reward as this transitions occur, we propose to model it as a \textit{game} between the decision maker and a player called \textit{Nature} which will select his actions from the causal model.

>>>>

While the standard setting in RL is to model the interaction agent-environment as an agent that moves from one \textit{state} to another inside a model of the environment and observing a reward as these transitions occur, we propose to model it as a \textit{game} between the decision maker and a player called \textit{Nature} which will select his actions from the causal model.
